### 2015-02-22 fundamentals/conclusion.tex
Comments on things we say about VISION, et al

The \Cyclus nuclear fuel cycle framework presents a more generic and flexible
alternative to existing fuel cycle simulators. Where previous nuclear fuel cycle simulators have had limited distribution,
uncertain provenance, and restricted customizability, \Cyclus emphasizes an
open access and development strategy.  Open development, with transparent
publication of the source code, not only provides much-needed accessibility,
but also enables transparency and community oversight.

>>>>

% gonuke: I am sensitive to making the implication that VISION (or others) has
%         ``uncertain provenance''.  It's not that I disagree with that
%         sentiments, but this can imagine this being perceived as a pretty
%         strong accusation and we better be prepared to back it up, or reword
%         it slightly.

The \Cyclus nuclear fuel cycle framework presents a more generic and flexible
alternative to existing fuel cycle simulators. Where previous nuclear fuel cycle simulators have had limited distribution,
constrained simulation capabilities, and restricted customizability, \Cyclus emphasizes an
open access and development strategy.  Open development, with transparent
publication of the source code, not only provides much-needed accessibility,
but also enables transparency and community oversight.
